---
title: "Week 4 - Wednesday"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Please finish reading chapter 6 of "An Introduction to Statistical Learning". The chapter covers Shrinkage methods including ridge and lasso regression.

This will be a good time to finally talk about hyper parameter tuning. We will use the [tune](https://tune.tidymodels.org/) package and [dials](https://dials/tidymodels.org/) package. A great place to start learning about these packages is [this post](https://tune.tidymodels.org/articles/getting_started.html).

The tidymodels labs chapter can be found [here](https://emilhvitfeldt.github.io/ISLR-tidymodels-labs/linear-model-selection-and-regularization.html).

## Slides

```{r embed-xaringan, echo=FALSE, eval=TRUE}
xaringanExtra::embed_xaringan(url = "static/slides/week4-wednesday/index.html", ratio = "16:9")
```

[PDF download](static/slides/week4-wednesday/week4-wednesday.pdf) [Full Screen](static/slides/week4-wednesday/index.html)
