---
title: "Week 1 - Monday"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

Read chapter 2 of "An Introduction to Statistical Learning". This is a big picture chapter that lays the foundation of the rest of the book. It is not expected to have read this before class.

Chapter 1 serves as an introduction to the book, data, and notation. Can be read or skimmed through if you want.

We will be using [R](https://cran.r-project.org/) which can be downloaded [here](https://cran.r-project.org/). Additionally, it is also advised to use [RStudio](https://rstudio.com/) which can be downloaded [here](https://rstudio.com/products/rstudio/download/#download), but any [IDE](https://en.wikipedia.org/wiki/Integrated_development_environment) will work.

We will be using the [tidymodels](https://www.tidymodels.org/) ecosystem of packages designed for modeling. If you haven't already you should install these packages along with [tidyverse](https://www.tidyverse.org/).

```{r}
install.packages("tidymodels")
install.packages("tidyverse")
```

We will also be using the developmental version of [parsnip](https://parsnip.tidymodels.org/) which can be installed with

```{r}
#install.packages("devtools")
devtools::install_github("tidymodels/parsnip")
```

## Slides

```{r embed-xaringan, echo=FALSE, eval=TRUE}
xaringanExtra::embed_xaringan(url = "static/slides/week1-monday/index.html", ratio = "16:9")
```

[PDF download](static/slides/week1-monday/week1-monday.pdf) [Full Screen](static/slides/week1-monday/index.html)
