---
title: "Week 1 - Wednesday"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval=FALSE)
```

Read chapter 3 of "An Introduction to Statistical Learning". This chapter goes over simple linear regression, multiple linear regression, and the considerations used in linear regression. As far as I can tell, you have all taken courses where linear regression has been introduced. It is still worthwhile for you to read this chapter to get familiar with the book, and hopefully, it will be an easy read.

If you want more information on the theoretical background you can read sections 3.1 and 3.2 of "The Elements of Statistical Learning". This is optional reading.

Instead of reading the lab sections of chapter 3, read [this](https://emilhvitfeldt.github.io/ISLR-tidymodels-labs/linear-regression.html) chapter instead which I rewrote to use tidymodels.


## Slides

```{r embed-xaringan, echo=FALSE, eval=TRUE}
xaringanExtra::embed_xaringan(url = "static/slides/week1-wednesday/index.html", ratio = "16:9")
```

[PDF download](static/slides/week1-wednesday/week1-wednesday.pdf) [Full Screen](static/slides/week1-wednesday/index.html)
