---
title: "Schedule"
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
library(glue)
library(fs)
library(stringr)

link_generator <- function(name) {
  function(x) {
    if (file_exists(glue("{name}-{x}.Rmd"))) {
      url <- glue("{name}-{x}.html")
      return(glue("[{name}]({url})"))
    } else {
      return(glue("[{str_to_title(name)} haven't been posted yet]()"))
    }
  }
}

readings <- link_generator("readings")
labs <- link_generator("labs")
assignments <- link_generator("assignments")
```

```{r}
library(lubridate)
first_week <- date(c("2021-05-17", "2021-05-23"))

week_days <- function(x) {
  days <- first_week %m+% days((x - 1) * 7)
  glue("*{days[1]} to {days[2]}*")
}
```

# Week 1

`r week_days(1)`

`r assignments("week1")`

### Monday 5-17

Topics: Introductions, What is Statistical Machine Learning?, R, RStudio, Tidymodels

`r readings("week1-monday")`

`r labs("week1-monday")`

### Wednesday 5-19

Topics: Linear regression, Regression

`r readings("week1-wednesday")`

`r labs("week1-wednesday")`

# Week 2

`r week_days(2)`

`r assignments("week2")`

### Monday 5-24

Topics: Logistic Regression, Classification, Train-Test Split

`r readings("week2-monday")`

`r labs("week2-monday")`

### Wednesday 5-26

Topics: LDA, QDA, K-Nearest Neighbors

`r readings("week2-wednesday")`

`r labs("week2-wednesday")`

# Week 3

`r week_days(3)`

`r assignments("week3")`

### Monday 6-02

Topics: Bootstrap, Model Diagnostics, Evaluation Metrics, Cross Validation

`r readings("week3-wednesday")`

`r labs("week3-wednesday")`

### Wednesday 6-05

Topics: Feature Engineering, Data Preprocessing, Clustering, K-Means Clustering, Hierarchical Clustering

`r readings("week3-saturday")`

`r labs("week3-saturday")`

# Week 4

`r week_days(4)`

`r assignments("week4")`

### Monday 6-07

Topics: PCA, PCA Regression

`r readings("wee4-monday")`

`r labs("week4-monday")`

### Wednesday 6-09

Topics: Shrinkage Methods, Rigde, Lasso, Hyper Parameter Tuning

`r readings("week4-wednesday")`

`r labs("week4-wednesday")`

# Week 5

`r week_days(5)`

`r assignments("week5")`

### Monday 6-14

Topics: Splines, GAM

`r readings("wee5-monday")`

`r labs("week5-monday")`

### Wednesday 6-16

Topics: Decision Trees, Bagging, Boosting, Random Forrests

`r readings("week5-wednesday")`

`r labs("week5-wednesday")`

# Week 6

`r week_days(6)`

No Assignment this week. just final project.

### Monday 6-21

Topics: SVM

`r readings("wee5-monday")`

`r labs("week5-monday")`

### Wednesday 06-23

Topics: Final Project Presentations
